Quantifying sablefish movement in the northeast Pacific

### 2022-01-29 ms/manuscript.tex
git subrepo pull ms
subrepo:
  subdir:   "ms"
  merged:   "6370b25"
upstream:
  origin:   "https://git.overleaf.com/5eb078b74a86f80001efc257"
  branch:   "master"
  commit:   "6370b25"
git-subrepo:
  version:  "0.4.3"
  origin:   "https://github.com/ingydotnet/git-subrepo"
  commit:   "2f68596"
git subrepo pull (merge) ms
subrepo:
  subdir:   "ms"
  merged:   "81495a6"
upstream:
  origin:   "https://git.overleaf.com/5eb078b74a86f80001efc257"
  branch:   "master"
  commit:   "2371c75"
git-subrepo:
  version:  "0.4.3"
  origin:   "https://github.com/ingydotnet/git-subrepo"
  commit:   "2f68596"

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{bm}
\usepackage{lineno}
\renewcommand\linenumberfont{\normalfont\bfseries\small\color{darkgrey}}
\usepackage{booktabs}
\usepackage[round]{natbib}
\bibliographystyle{plainnat}
\usepackage{authblk}
% Linux Libertine:
\usepackage{textcomp}
\usepackage[sb]{libertine}
\usepackage[varqu,varl]{inconsolata}% sans serif typewriter
\usepackage[libertine,bigdelims,vvarbb]{newtxmath} % bb from STIX
\usepackage[cal=boondoxo]{mathalfa} % mathcal
\useosf % osf for text, not math
\usepackage[supstfm=libertinesups,%
  supscaled=1.2,%
  raised=-.13em]{superiors}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage[section]{placeins} % Keep floats (figs, tabs, eqns) in the right section
% I assume these all work together to make nice colour
\usepackage[dvipsnames]{xcolor}
\definecolor{niceblue}{HTML}{236899} % Depends \usepackage[dvipsnames]{xcolor}
\definecolor{darkgrey}{HTML}{A9A9A9} % Depends \usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=niceblue,
    citecolor=niceblue,
    linkbordercolor = white
}
% End nice colour
\usepackage{pgfplotstable} % For tables
\pgfplotsset{compat=1.16} % For tables
\input{./values/values}
\usepackage{graphicx}
\graphicspath{ {./figs/} }
\newcommand{\lr}[1]{{\color{blue}#1}}
% \newcommand{\bc}[1]{{\color{red}#1}}

@@

\subsection{Questions}
\begin{enumerate}
    \item How much do sablefish move among geographic regions? 
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:heat-region-average-pooled}
            \item Notes: standard data and priors
        \end{itemize}
    \item How sensitive are sablefish transition rates to alternative reporting rate assumptions?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:bar-sensitivity-reporting} (SI)
            \item Notes: six model fits---33\% increase or 50\% decrease for one region in each fit
        \end{itemize}
    \item How sensitive are sablefish transition rates to harvest rate priors?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: TODO scatterplot; one panel per region; retention (and CIs) vs harvest prior sd multiplier (SI)
            \item Notes: five model fits; harvest rate prior sd scaled to mean by progressively wider multiplier
        \end{itemize}    
    \item How much do sablefish transition rates vary by length class?
        \begin{itemize}
            \item Model: \texttt{region-average-length}
            \item Visual: \autoref{fig:heat-region-average-length} (SI)
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-pooled}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs season  
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by year?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs year  
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates by length class vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-length}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs season (SI)
            \item Notes: standard data and priors
        \end{itemize}
    \item How many sablefish moved between regions each year?
        \begin{itemize}
            \item Model: \texttt{region-year-length}
            \item Visual: TODO barplot; one panel per border; directional (bars) and net (line) movement
            \item Notes: standard data and priors; abundance at length data (scaled proportional to survey biomass index for Alaska regions)
        \end{itemize}    
    \item What is the relationship between sablefish density and transition rates?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: TBD
            \item Notes: TBD ideally use annual biomass estimates as proxy for relative density
        \end{itemize}    
    \item Does the movement model recover known parameters on simulated data adequately?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: TBD
            \item Notes: TBD
        \end{itemize}
\end{enumerate}

@@

@@

\newpage
\bibliography{refs}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{bm}
\usepackage{lineno}
\renewcommand\linenumberfont{\normalfont\bfseries\small\color{darkgrey}}
\usepackage{booktabs}
\usepackage[round]{natbib}
\bibliographystyle{plainnat}
\usepackage{authblk}
% Linux Libertine:
\usepackage{textcomp}
\usepackage[sb]{libertine}
\usepackage[varqu,varl]{inconsolata}% sans serif typewriter
\usepackage[libertine,bigdelims,vvarbb]{newtxmath} % bb from STIX
\usepackage[cal=boondoxo]{mathalfa} % mathcal
\useosf % osf for text, not math
\usepackage[supstfm=libertinesups,%
  supscaled=1.2,%
  raised=-.13em]{superiors}
\usepackage{setspace}
\usepackage{siunitx}
\usepackage[section]{placeins} % Keep floats (figs, tabs, eqns) in the right section
% I assume these all work together to make nice colour
\usepackage[dvipsnames]{xcolor}
\definecolor{niceblue}{HTML}{236899} % Depends \usepackage[dvipsnames]{xcolor}
\definecolor{darkgrey}{HTML}{A9A9A9} % Depends \usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=black,      
    urlcolor=niceblue,
    citecolor=niceblue,
    linkbordercolor = white
}
% End nice colour
\usepackage{pgfplotstable} % For tables
\pgfplotsset{compat=1.16} % For tables
\input{./vals/values}
\usepackage{graphicx}
\graphicspath{ {./figs/} }
\newcommand{\lr}[1]{{\color{blue}#1}}
% \newcommand{\bc}[1]{{\color{red}#1}}

@@

\subsection{Questions}
\begin{enumerate}
    \item How much do sablefish move among geographic regions? 
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:heat-region-average-pooled}
            \item Notes: standard data and priors
        \end{itemize}
    \item How sensitive are sablefish transition rates to alternative reporting rate assumptions?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:bar-sensitivity-reporting} (SI)
            \item Notes: six model fits---33\% increase or 50\% decrease for one region in each fit
        \end{itemize}
    \item How sensitive are sablefish transition rates to harvest rate priors?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: \autoref{fig:bar-sensitivity-harvest-priors} (SI)
            \item Notes: five model fits; harvest rate prior sd scaled to mean by progressively wider multiplier
        \end{itemize}    
    \item How much do sablefish transition rates vary by length class?
        \begin{itemize}
            \item Model: \texttt{region-average-length}
            \item Visual: \autoref{fig:heat-region-average-length} (SI)
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-pooled}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs season  
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates vary by year?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs year  
            \item Notes: standard data and priors
        \end{itemize}    
    \item How much do sablefish transition rates by length class vary by season?
        \begin{itemize}
            \item Model: \texttt{region-season-length}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs season (SI)
            \item Notes: standard data and priors
        \end{itemize}
    \item How much do sablefish transition rates by length class vary by year?
        \begin{itemize}
            \item Model: \texttt{region-year-length}
            \item Visual: TODO scatterplot matrix; transition rate (and CI) vs year (SI) 
            \item Notes: standard data and priors
        \end{itemize} 
    \item How many sablefish moved between regions each year?
        \begin{itemize}
            \item Model: \texttt{region-year-length}
            \item Visual: TODO barplot; one panel per border; directional (bars) and net (line) movement
            \item Notes: standard data and priors; abundance at length data (scaled proportional to survey biomass index for Alaska regions)
        \end{itemize}    
    \item What is the relationship between sablefish density and transition rates?
        \begin{itemize}
            \item Model: \texttt{region-year-pooled}
            \item Visual: TBD
            \item Notes: TBD ideally use annual biomass estimates as proxy for relative density
        \end{itemize}    
    \item Does the movement model recover known parameters on simulated data adequately?
        \begin{itemize}
            \item Model: \texttt{region-average-pooled}
            \item Visual: TBD
            \item Notes: TBD
        \end{itemize}
\end{enumerate}

@@

% bar-sensitivity-harvest-priors
\begin{figure}[htb]
    \centering
    \includegraphics[width = 0.7\textwidth]{bar-sensitivity-harvest-priors.png}
    \caption{}
    \label{fig:bar-sensitivity-harvest-priors}
\end{figure}

@@

\newpage
\bibliography{refs/refs}
